\LARGE \bf How Children Perceive and Interact with a Robot that Behaves Unexpectedly

### 2014-10-03 paper.tex
Lastest minor fixes, reported by Julia

While we found only a limited recognition of the different misbehaviours of the
robot that we attribute to the age of the child participants (M=4.46),
interesting findings include a sustained engagement level, an unexpectedly low
level of attribution of higher cognitive abilities and a \emph{negative}
correlation between anthropomorphic projections and actual behavioural
engagement.

@@

This study also aims at assessing the effectiveness of the \emph{anthropomorphic
index} proposed by Fink \etal\cite{fink2014dynamics} as a compound (behavioural
and phenomenological) metric for the attribution of human-like features to
a robot. We are especially interested in investigating how this indicator predicts
and/or reflects actual \emph{engagement} in the interaction.

@@

We analyse child-robot interaction with a robot that shows unexpected behaviour.
In a playful scenario which was set up in a laboratory environment, 26 children
aged 4-5 years (MD=4.46) were assembling a domino game together. Each group
consisted of two children and the \emph{Ranger} robot, which was used to
transport domino tiles between the two children.

@@

\paragraph{Moral standing}

>>>>

While we found only a limited recognition of the different misbehaviours of the
robot that we attribute to the age of the child participants (4-5 years old),
interesting findings include a sustained engagement level, an unexpectedly low
level of attribution of higher cognitive abilities and a \emph{negative}
correlation between anthropomorphic projections and actual behavioural
engagement.

@@

This study also aims at assessing the effectiveness of the \emph{anthropomorphic
index} proposed in~\cite{fink2014dynamics} as a compound (behavioural
and phenomenological) metric for the attribution of human-like features to
a robot. We are especially interested in investigating how this indicator predicts
and/or reflects actual \emph{engagement} in the interaction.

@@

We analyse child-robot interaction with a robot that shows unexpected behaviour.
In a playful scenario which was set up in a laboratory environment, 26 children
aged 4-5 years (M=4.46) were assembling a domino game together. Each group
consisted of two children and the \emph{Ranger} robot, which was used to
transport domino tiles between the two children.

@@

\vspace{1em}
\paragraph{Moral standing}
